A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-13 manuscript.Rmd
small changes after reading

There are probably few things as frustrating as realizing that the data that you gathered cannot answer the research question you had in mind.
A step to prevent unpleasant surprises is to simulate data.
The machine learning community has begun to use simulated data to test models and their implementation [@braiekTestingMachineLearning2020].
Beyond checking the technical side of the model, simulation is also beneficial on a conceptual level [@axelrodAdvancingArtSimulation1997].
Simulated data lets you verify that the data you expect to gather and the analysis you plan fit together.
Beyond ensuring that the code runs without technical error and it lets you form more realistic expectations about the estimates' correctness and precision.
No matter which analytic strategy you plan, it comes with assumptions and a simulation forces you to address these assumptions more directly than simply thinking about them.
If you identify unrealistic assumptions, you can either violate these assumptions and see if the analytic strategy is robust or modify the analytical approach to address them.
We will show an example using structural equation modeling (SEM) for our Machiavellism example.
However, the general process applies to any statistical model, but the simulation here is specific to our hypothetical research question.
One has to make many educated guesses to simulate data that closely matches your expectation.
These guesses strongly depend on the study you are planning, and there cannot be a one fits all solution.
The analytic strategy (i.e. SEM) often gives you a hint about how to simulate data.

@@

[^gh-repo2]: https://github.com/aaronpeikert/repro-tutorial
[^gh-repo3]: https://github.com/aaronpeikert/reproducible-research
## Closed Data (optional)

>>>>

There are probably few things as frustrating as realizing that the data that you gathered cannot answer the research question you had in mind.
A step to prevent unpleasant surprises is to simulate data.
The machine learning community has begun to routinely simulate data to test models and their implementation [@braiekTestingMachineLearning2020].
Beyond checking the technical side of the model, simulation is also beneficial on a conceptual level [@axelrodAdvancingArtSimulation1997].
Simulated data lets you verify that the data you expect to gather and the analysis you plan fit together.
Beyond ensuring that the code runs without technical error and it lets you form more realistic expectations about the estimates' correctness and precision.
No matter which analytic strategy you plan, it comes with assumptions and a simulation forces you to address these assumptions more directly than simply thinking about them.
If you identify unrealistic assumptions, you can either violate these assumptions and see if the analytic strategy is robust or modify the analytical approach to address them.
We will show an example using structural equation modeling (SEM) for our Machiavellism example.
However, the general process applies to any statistical model, but the simulation here is specific to our hypothetical research question.
One has to make many educated guesses to simulate data that closely matches your expectation.
These guesses strongly depend on the study you are planning, and there cannot be a one fits all solution.
The analytic strategy (i.e. SEM) often gives you a hint about how to simulate data.

@@

[^gh-repo2]: https://github.com/aaronpeikert/repro-tutorial
[^gh-repo3]: https://github.com/aaronpeikert/reproducible-research

## Closed Data (optional)
